Learning by Teaching a Robot:\\The Case of Handwriting

### 2015-07-10 main.tex
re-writing henry part

\subsubsection{Context, Study Design}
Thomas is a five and half years old child. It is followed by an occupational
therapist. According to the therapist, he presents visuo-constructive deficits.
From our perspective, the main effect of this trouble during handwriting
activity was that Thomas
did not have any mental template to draw the shape of a letter. So he was 
apparently performing random attempts and then was comparing with the provided template.
What is more, Thomas is strongly careless : he rarely payed attention to
advices, even to what he was doing when he was currently drawing, and he was
quickly shifting his attention from one
activity to another.
Hence, the goal of this study is to face those two challenging issues
(visuo-constructive deficits and inattention) in order to keep Thomas focused
on the activity during forty-minutes interactions, and to make the robot
evidently learning from his demonstrations.\\

This experiment took place in the therapist's office. It was divided in four
sessions as well. This time, we assumed that a scenario like the one we used for Vincent was
no longer relevant with Thomas. We just introduced the robot and quickly
said that it was seeking help to train for a robot handwriting contest.\\

@@

Since Thomas was frequently drawing horizontally inverted numbers, or even
absolutely unrecognizable shapes, we programmed the robot to refuse shapes that
was too distant to a reference with a threshold we arbitrary fixed. In that way,
the child was forced to take care on what he was providing to the robot as
demonstration. Also, to make sure the robot was going to improve its handwriting
and to clearly show this improvement, we decided to make it absolutely starting
from scratch : for all numbers, the first try of the robot resulted in
a simple vertical stroke (see the first robot's try in~\ref{learning_6_demos}).

@@

\subsubsection{Results}
Despite his inattention, Thomas was able to keep on the activity during more than
forty minutes in each session.\\

As soon as Thomas understood that the robot was only accepting recognizable
shapes, he started to take care on the shapes he was providing to it. He used the
clearing button to retry when he judged that his numbers where not going to be
accepted by the robot. According to the therapist, it was the first time Thomas
was intrinsically correcting himself.\\

Since the robot was learning from scratch, each time Thomas succeeded to make his
demonstrations accepted by it, the improvement of its handwriting was
obvious~\ref{learning_6_demos},~\ref{henry_distances}.
Therefor, Thomas quickly enter in an self-rewarding game where the rewards were
the improvement of the robot. Over the three last sessions he provided 99
demonstrations of number shapes to the robot.

>>>>

\subsubsection{Context, Study Design}

This study focused technical adaptations of the CoWriter activity for a
child diagnosed with real writing deficits.\\

Thomas is a six years old child. It is under the care of an occupational
therapist. According to the therapist, he shows visuo-constructive deficits.
As an effect in writing activities, he was frequently performing random attempts and then was comparing
with the provided template. What is more, Thomas is strongly careless : he rarely payed attention to
advices, even to what he was doing when he was currently drawing, and he was
quickly shifting his attention from one
activity to another.\\

Our objective is to investigate small modifications of the activity adapted to
the troubles of Thomas (visuo-constructive deficits and inattention) in order to
sustain him focused
on the activity during forty-minutes session, and to make the robot
evidently learning from his demonstrations.\\

The experiment took place in the therapist's office. It was divided in four
sessions. This time, we assumed that a scenario like the one we used for Vincent was
no longer relevant with Thomas. We just introduced the robot and quickly
said that it was seeking help to train for a robot handwriting contest.\\

@@

Since Thomas was frequently drawing horizontally-inverted numbers, or even
unrecognizable allographs, the learning algorithm of the robot was converging to
meaningless scrawls. To fix this problem, we programmed the robot to refuse allographs that
were too distant to a reference with a threshold we arbitrary fixed. In that way,
the child was forced to take care on what he was providing to the robot as
demonstration. Also, to make sure the robot was going to improve its handwriting
and to clearly show this improvement, we decided to make it starting
from scratch : for all numbers, the first try of the robot resulted in
a simple vertical stroke (see the first robot's try
in~\ref{learning_6_demos}).\\

In this setup, we added a second tablet with one button per numbers. It was used
by the child to chose a new number to teach to the robot. It also provided the
possiblity to enter letters or words, and to switch to another activity (the
robot telling a story).

@@

\subsubsection{Results}

Despite his inattention, Thomas was able to keep on the activity during more than
forty minutes in each session. In total, 55 allographs out of 82 
provided by the child as demonstration were acceptable by the robot (with a
progressive improvement from 13 out of 28 in the first session up to 26 out
of 29 in the last session).\\

As soon as Thomas understood that the robot was only accepting recognizable
allographs, he started to take care on the allographs he was providing to it. He used the
clearing button to retry when he judged that his numbers where not going to be
accepted by the robot. According to the therapist, it was the first time Thomas
was intrinsically correcting himself.\\

Since the robot was learning from scratch, each time Thomas succeeded to make his
demonstrations accepted by it, the improvement of its handwriting was
visible~\ref{learning_6_demos},~\ref{henry_distances}.
Therefor, Thomas quickly entered in an self-rewarding game where the rewards were
the improvements of the robot, that enhanced his attention.
